<div align="center">
 <marquee behavior="alternate" bgcolor="#bb3434" direction="left" height:="" 
 loop="7" scrollamount="1" scrolldelay="2" width="100%">
 <span style="font-size: 20px;color:#FFFFFF">
 Intro to R and Data Frames!</span></marquee>
</div>

---
title: "Homework 1"
author: "Bob Bartolini"
date: "9/18/2020"
output: html_document

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
options(width = 60)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x, options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"', options$max.height)
    )
    hook_output(x, options)
  })
})
```



#  <span style="color: green;">  Let’s explore the dataset quakes looking at earthquakes off of Fiji. </span> 
# [**GIT**](https://github.com/rjmaitri/Data-Analysis/blob/master/01_Bartolini_Bob_2020.Rmd)

#### 1. Load quakes with data(quakes). Show what’s there with str() and summary().

```{r}
#load the data for earthquakes off of Fiji
data(quakes)
#check the structure of the quakes dataset
str(quakes)

```

```{r}
#summarize the quakes data set
summary(quakes)
```

#### 2. Show the entirity of the column long.

```{r, max.height = '150px'}
#Extract the column long from quakes
quakes$long

```

#### 3. Hey, another useful function - unique()! Apply it to a vector, and you can see what are all of the unique values. It’s great for really digging into a problematic vector. 
#### What unique stations are there? Use length() with unique() to determine how many stations there are.

```{r, max.height = '150px'}

#Extract the unique station ID's
unique(quakes$stations)

#Determine the amount of unique station ID's
length(unique(quakes$stations))

```


#### 4. Using range(), what is the range of depths where quakes occur?

```{r}
#Extract the range of depths where quakes occur
range(quakes$depth)

```

#### Extra Credit
E.C. Where was the earthquake of largest magnitude found? You’ll need to use come comparisons and the max() function for this in your indices instead of a number!

```{r}

#Extract the station with the highest magnitude earthquake
quakes$stations[max(quakes$mag)]
#Extract the latitude of that station
quakes$lat[quakes$stations[max(quakes$mag)]]
#Extract the longitude of the station
quakes$long[quakes$stations[max(quakes$mag)]]

```
